---
title: R API client for the Lamin API
format: gfm
---

## Installation

To install directly from Github, use `remotes`:
```R
if (!requireNamespace("remotes", quietly=TRUE)) {
    install.packages("remotes")
}
remotes::install_github("data-intuitive/laminr.api")
```

### Usage

```{r}
library(laminr.api)

api_url <- getOption("lamindb_current_instance")$api_url
instance_id <- getOption("lamindb_current_instance")$id
schema_id <- getOption("lamindb_current_instance")$schema_id

api_client <- ApiClient$new(base_path = api_url)

api <- DefaultApi$new(api_client = api_client)
```

Show API object:

```{r}
api
```

Get schema:

```{r}
schema <- api$GetSchemaInstancesInstanceIdSchemaGet(instance_id)
names(schema)
names(schema$core)
```

Get record:

```{r}
api$GetRecordInstancesInstanceIdModulesModuleNameModelNameIdOrUidPost(
  instance_id,
  "core",
  "artifact",
  "KBW89Mf7IGcekja2hADu",
  schema_id,
  include_foreign_keys = TRUE
)
```

## Documentation for API Endpoints

All URIs are relative to *http://localhost*

Class | Method | HTTP request | Description
------------ | ------------- | ------------- | -------------
*DefaultApi* | [**AddCollaboratorInstancesInstanceIdCollaboratorsAccountIdPut**](docs/DefaultApi.md#AddCollaboratorInstancesInstanceIdCollaboratorsAccountIdPut) | **PUT** /instances/{instance_id}/collaborators/{account_id} | Add Collaborator
*DefaultApi* | [**CreateInstanceInstancesPut**](docs/DefaultApi.md#CreateInstanceInstancesPut) | **PUT** /instances | Create Instance
*DefaultApi* | [**CreateRecordInstancesInstanceIdModulesModuleNameModelNamePut**](docs/DefaultApi.md#CreateRecordInstancesInstanceIdModulesModuleNameModelNamePut) | **PUT** /instances/{instance_id}/modules/{module_name}/{model_name} | Create Record
*DefaultApi* | [**DeleteCollaboratorInstancesInstanceIdCollaboratorsAccountIdDelete**](docs/DefaultApi.md#DeleteCollaboratorInstancesInstanceIdCollaboratorsAccountIdDelete) | **DELETE** /instances/{instance_id}/collaborators/{account_id} | Delete Collaborator
*DefaultApi* | [**DeleteInstanceInstancesInstanceIdDelete**](docs/DefaultApi.md#DeleteInstanceInstancesInstanceIdDelete) | **DELETE** /instances/{instance_id} | Delete Instance
*DefaultApi* | [**DeleteRecordInstancesInstanceIdModulesModuleNameModelNameUidDelete**](docs/DefaultApi.md#DeleteRecordInstancesInstanceIdModulesModuleNameModelNameUidDelete) | **DELETE** /instances/{instance_id}/modules/{module_name}/{model_name}/{uid} | Delete Record
*DefaultApi* | [**GeneratePasswordInstancesInstanceIdDbPasswordGet**](docs/DefaultApi.md#GeneratePasswordInstancesInstanceIdDbPasswordGet) | **GET** /instances/{instance_id}/db/password | Generate Password
*DefaultApi* | [**GenerateUrlInstancesInstanceIdDbUrlGet**](docs/DefaultApi.md#GenerateUrlInstancesInstanceIdDbUrlGet) | **GET** /instances/{instance_id}/db/url | Generate Url
*DefaultApi* | [**GetInstanceStatisticsInstancesInstanceIdStatisticsGet**](docs/DefaultApi.md#GetInstanceStatisticsInstancesInstanceIdStatisticsGet) | **GET** /instances/{instance_id}/statistics | Get Instance Statistics
*DefaultApi* | [**GetNonEmptyTablesInstancesInstanceIdNonEmptyTablesGet**](docs/DefaultApi.md#GetNonEmptyTablesInstancesInstanceIdNonEmptyTablesGet) | **GET** /instances/{instance_id}/non_empty_tables | Get Non Empty Tables
*DefaultApi* | [**GetRecordInstancesInstanceIdModulesModuleNameModelNameIdOrUidPost**](docs/DefaultApi.md#GetRecordInstancesInstanceIdModulesModuleNameModelNameIdOrUidPost) | **POST** /instances/{instance_id}/modules/{module_name}/{model_name}/{id_or_uid} | Get Record
*DefaultApi* | [**GetRecordsInstancesInstanceIdModulesModuleNameModelNamePost**](docs/DefaultApi.md#GetRecordsInstancesInstanceIdModulesModuleNameModelNamePost) | **POST** /instances/{instance_id}/modules/{module_name}/{model_name} | Get Records
*DefaultApi* | [**GetRelationsInstancesInstanceIdSchemaModuleNameModelNameGet**](docs/DefaultApi.md#GetRelationsInstancesInstanceIdSchemaModuleNameModelNameGet) | **GET** /instances/{instance_id}/schema/{module_name}/{model_name} | Get Relations
*DefaultApi* | [**GetSchemaInstancesInstanceIdSchemaGet**](docs/DefaultApi.md#GetSchemaInstancesInstanceIdSchemaGet) | **GET** /instances/{instance_id}/schema | Get Schema
*DefaultApi* | [**GetValuesInstancesInstanceIdModulesModuleNameModelNameFieldsFieldPathPost**](docs/DefaultApi.md#GetValuesInstancesInstanceIdModulesModuleNameModelNameFieldsFieldPathPost) | **POST** /instances/{instance_id}/modules/{module_name}/{model_name}/fields/{field_path} | Get Values
*DefaultApi* | [**GrantS3PermissionsStoragesS3BucketNamePermissionsPut**](docs/DefaultApi.md#GrantS3PermissionsStoragesS3BucketNamePermissionsPut) | **PUT** /storages/s3/{bucket_name}/permissions | Grant S3 Permissions
*DefaultApi* | [**GroupByInstancesInstanceIdModulesModuleNameModelNameGroupByPost**](docs/DefaultApi.md#GroupByInstancesInstanceIdModulesModuleNameModelNameGroupByPost) | **POST** /instances/{instance_id}/modules/{module_name}/{model_name}/group-by | Group By
*DefaultApi* | [**TransferOwnershipInstancesInstanceIdOwnerHandlePatch**](docs/DefaultApi.md#TransferOwnershipInstancesInstanceIdOwnerHandlePatch) | **PATCH** /instances/{instance_id}/owner/{handle} | Transfer Ownership
*DefaultApi* | [**UpdateCollaboratorInstancesInstanceIdCollaboratorsAccountIdPatch**](docs/DefaultApi.md#UpdateCollaboratorInstancesInstanceIdCollaboratorsAccountIdPatch) | **PATCH** /instances/{instance_id}/collaborators/{account_id} | Update Collaborator
*DefaultApi* | [**UpdateRecordInstancesInstanceIdModulesModuleNameModelNameUidPatch**](docs/DefaultApi.md#UpdateRecordInstancesInstanceIdModulesModuleNameModelNameUidPatch) | **PATCH** /instances/{instance_id}/modules/{module_name}/{model_name}/{uid} | Update Record


## Documentation for Models

 - [Dimension](docs/Dimension.md)
 - [GetRecordRequestBody](docs/GetRecordRequestBody.md)
 - [GetRecordsRequestBody](docs/GetRecordsRequestBody.md)
 - [GetValuesRequestBody](docs/GetValuesRequestBody.md)
 - [GroupByRequestBody](docs/GroupByRequestBody.md)
 - [HTTPValidationError](docs/HTTPValidationError.md)
 - [Measure](docs/Measure.md)
 - [OrderByColumn](docs/OrderByColumn.md)
 - [S3PermissionsRequest](docs/S3PermissionsRequest.md)
 - [ValidationError](docs/ValidationError.md)
 - [ValidationErrorLocInner](docs/ValidationErrorLocInner.md)


## Documentation for Authorization

Endpoints do not require authorization.
